# Base R syntax and data type

## Data type
  + Charactor vector (srting and/ or factor): defined by using " "
    + (e.g.) "Jack", "Rose"
    + Cannot perform mathmatical calculations
    
  + Numeric vector (double, integer etc...): numbers are written as is
    + (e.g.) 100, 200 
    + Can perfom a mathmatical calculations
  <br />
  + Logical vecor: TRUE or FALSE
      
Let's practice!

  * write a code *100 + 200* as a numerical vector
  * write a code *100 + 200* as a character vector

<iframe width='100%' height='400' src='https://rdrr.io/snippets/embed/?code=' frameborder='0'></iframe>
  

## Create a variable and assign a value 
* if you want to make a variable x and assign 1 as a value
    + "<-" is the symbol we use to assign values in R
    + "#" is to make comments on an R script
```{r, eval=FALSE, include=TRUE, message=FALSE}
x <- 1
x #check the variable
```

Let's practice!

  * Create a variable pineapples and assign 120 as a value
      + Check the variable
  
<iframe width='100%' height='400' src='https://rdrr.io/snippets/embed/?code=' frameborder='0'></iframe>

## Create variables and calculate
* Create variables x and y. 
* Assign 1 as a value for x, 4 as a value of y
* Add them up
* Check if x is bigger than y

```{r, eval=FALSE, include=TRUE, message=FALSE}

#create variables x, y and assign values
x <- 1
y <- 4

#add x and y
x + y

#examine using logical operator 
x > y

```
Let's practice!

* Create a variable pineapples and assign 120 as a value. 
* Create a variable strawberries and assign 70 as a value.
* Add them up using variable names
* Check if pineapples are larger than strawberries using a logical operator

<iframe width='100%' height='400' src='https://rdrr.io/snippets/embed/?code=' frameborder='0'></iframe>


## Create a new variable with the sum 
* Create a variable z and assign the sum of x + y
```{r, eval=FALSE, include=TRUE, message=FALSE}
x <- 1
y <- 4

#create a new variable z and assign the sum of x and y
z <- x + y

#check the value of z
z
``` 
Let's practice!

* Create a variable pineapples and assign 120 as a value. 
* Create a variable strawberries and assign 70 as a value.
* Create a new variable pineberries and assign the sum of pineapples and strawberries
* Check the value of pineberries)

<iframe width='100%' height='400' src='https://rdrr.io/snippets/embed/?code=' frameborder='0'></iframe>

## Use functions
* Calcurate the sum of x, y and z 
```{r, eval=FALSE, include=TRUE, message=FALSE}
x <- 1
y <- 4
z <- x + y

#sum up x, y and z using the sum() function
sum(x, y, z)
```
Let's practice!

* Create a variable pineapples and assign 120 as a value. 
* Create a variable strawberries and assign 70 as a value.
* Create a new variable pineberries and assign the sum of pineapples and strawberries
* Sum up pinabbles, strawberries, and pineberries using the sum() function

<iframe width='100%' height='400' src='https://rdrr.io/snippets/embed/?code=' frameborder='0'></iframe>

## Make a data frame
* Make a data frame "df1"
    + (explanation 1). "variable" is a column name, c("", "",) is to add multiple vairiables. this says assign x to the "variable" column,  row 1. assign y to the "variable" column, row 2. assign z to the "variable" column, row 3. 
    + (explanation 2). "value" is a column name. this says that assign 1 to the "value" column, row 1. assign 4 to the "value" column, row 2. assign 10 to the "value" column, row 3. 
* Calcurate the mean of x, y and z 
```{r, eval=FALSE, include=TRUE, message=FALSE}
df1 <- data.frame("variable" = c("x", "y", "z"), #(explanation 1). 
                   "value" = c(1, 4, 10)) #(explanation 2). 

str(df1)

#calcurate mean
mean(df1$value) #"$" is select "value column" from df1
```

Let's practice!

* Create a dataframe "fruits," which contains two columns ("fruitType" and "amount")
    + pineapples, which the value is 120
    + strawberries, which the value is 70
    + pineberries, which the value is 190
* Check the structure of the dataframe 
* Calculate the mean of "amount"" 
    
<iframe width='100%' height='400' src='https://rdrr.io/snippets/embed/?code=' frameborder='0'></iframe>

## Create a simple plot

* Create a data frame "firstHalf"
* Create a simple barplot using the "barplot()" function
```{r, eval=FALSE, include=TRUE, message=FALSE}
firstHalf <- data.frame("month" = c("Jan", "Feb", "Mar", "Apr", "May", "June"), 
                   "value" = c(150, 200, 15, 70, 300, 60)) 

#create a bar plot. names.arg is to label each bar
barplot(fristHalf$value, names.arg = c("Jan", "Feb", "Mar", "Apr", "May", "June")) 
```

Let's practice!

* Create a data frame "secondHalf." Monthly values are as follows: 
    + July, 250
    + August, 10
    + September, 600
    + October, 120
    + November, 80
    + December, 50

* Create a barplot using the "barplot()" function
    + Make sure to label each bars
    
<iframe width='100%' height='400' src='https://rdrr.io/snippets/embed/?code=' frameborder='0'></iframe>

