# Practice Problem 1

## Let’s make Anscombe's quartet {-}

What is Anscombe's Quartet? 



General Steps for Data Analysis

1. Load data (of course, you need to have your data prior to this...)
2. Clean data 
3. Check data distributions
4. Data frame creation (subsetting the data)
5. Check data distribution 
    + Summary statistics 
    + Exploratory data visualization
6. Analyze your data 
7. Create a explanatory data visualization product


## Set up an environement and load data
  * Install R and R studio 
      + There are a couple options for R's Integrated Development Environment (IDE), but I would recommend R Studio if you do not have your preferred platform yet. 
  <br />
  <br />
  * Create an R peoject file (optional, but recommended)
      + name your file: myFirstR
  <br />
  <br />
  * Create an R script file
      + name your file: anscombe
  <br />
  <br />
  * Check and set up your work directory 
      + work directory: a place/ folder on your computer where your file locates
```{r, include=TRUE, eval=FALSE, message = FALSE}
#check your work directory
getwd()

#set your work directory 
setwd("/YOUR FILE PATH HERE/")

#mac users (if you made a folder on your desktop)
setwd("/Users/your-user-name/Desktop/myFirstR")

#PC users (if you made a folder on your desktop)
setwd("\\")
```

  * Install and load packages you need for the project
      + What are packages?
      + Difference between install and load packages 
          + Install packages: You only need to do it once when you don't have a package installed in your R
          + Load packages: You need to load them when you re-open R or want to use a package that is not loaded yet (package is already installed)
          + Make sure you install and load all the packages you need in the beginning of your code 
```{r, include=TRUE, eval=FALSE, message=FALSE}
#install packages 
install.packages("ggplot2")
install.packages("dyplyr")
install.packages("tidyverse")
install.packages("RCurl")
  
#load packages
library(ggplot2)
library(dplyr)
library(tidyverse)
library(RCurl)
```

```{r, include=TRUE, eval=FALSE, message=FALSE}
#to check installed packages, run the code below or click "packages" on R studio
ip = as.data.frame(installed.packages()[,c(1,3:4)])
ip = ip[is.na(ip$Priority),1:2,drop=FALSE]ip 
```
        
* load a dataset (if you are running R on R studio write this code to load data)
```{r, include=TRUE, eval=FALSE, message=FALSE}
#loading data from a github repository. assign URL variable
url <- getURL("https://raw.githubusercontent.com/maiuchi/r_test1/master/test.csv")

#name a data frame (df) anscombe and read csv
anscombe <- read.csv(text = url)
```

* R already has this data installed... so you can also do... 
```{r, include=TRUE, eval=FALSE, message=FALSE}
data("anscombe")
```

## Check data structure and clean data (done for today)

* Once you load the data up to R, the first thing you'd want to do is: 
    + Make sure your data is properly loaded 
        + function to use: View(name-of-dataframe)
    + Check the structure of the data
        + function to use: str(name-of-dataframe) or glimpse(name-of-dataframe)

## Check data distributions


